Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy

### 2024-05-07 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
doctoral qualification document

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")# 
source("../imagematrix.R")
source("../imagematrix1.R")
set.seed(1234567890, kind = "Mersenne-Twister")

@@

```{r Plot1, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r 2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
x1<-as.vector(cv_values)

@@

fit.weibull <- fitdist(x1, "weibull")
plot(fit.weibull)
fit.weibull$aic
# fit.norm <- fitdist(x1, "norm")
# fit.norm$aic
# plot(fit.norm)
```

@@

```{r cv5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland"}
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
alpha <- 5.452
beta <- 2.061

@@

#source("../imagematrix.R")
source("../imagematrix1.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
plot(imagematrix1(p_values_matrix ))
#plot(imagematrix(p_values_matrix >0.1))
```

```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```
```{r cv7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 7x7, Flevoland"}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
alpha <- 5.762
beta <- 2.611

@@

```{r cvOttawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}

@@

@@

```{r cqvOttawa_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}

@@

source("../imagematrix.R")
hist(p_values_matrix)
par(mfrow=c(1,2))
plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.05))
```
```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

@@

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "pink", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

>>>>

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")# 
source("../imagematrix.R")
#source("../imagematrix.R")
set.seed(1234567890, kind = "Mersenne-Twister")

@@

save(difference_values, x, file = "./Data/results_Lake_512_9W_AO_100b_36L.Rdata")
save(difference_values, x, file = "./Data/results_Lake_without_bootstrap.Rdata")
save(difference_values, x, file = "./Data/results_Lake_without_bootstrap1.Rdata")
load("./Data/results_mexico_600_9W_AO_100b_6L.Rdata")
```{r Plot_chicago_lake, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
#results_Chicago_1024_9_AO_100b_6L
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
load("../Programs/Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
#x1<-as.vector(epsilon_matrix)
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```{r Plot_ottawa_AO_300, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
#results_Chicago_1024_9_AO_100b_6L
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
load("../Programs/Data/results_pvalue_epsilon.Rdata")
#x1<-as.vector(epsilon_matrix)
source("../imagematrix.R")
hist(p_values_matrix)

ggplot() +
  geom_density(aes(x = as.vector(epsilon_matrix)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```{r normal2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR", eval=FALSE}
load("../Programs/Data/results_pvalue_epsilon.Rdata")
x1<-as.vector(epsilon_matrix)
#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
descdist(x1, discrete = FALSE)

#fit.weibull <- fitdist(x1, "weibull")
#plot(fit.weibull)
#fit.weibull$aic
 fit.norm <- fitdist(x1, "norm")
 fit.norm$aic
 plot(fit.norm)
```

```{r Plot_ottawa_AO_100, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
load("../Programs/Data/results_ottawa_city_512_7_AO_100b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```{r Plot_ottawa_ebra_50, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```
```{r Plot_ottawa_ebra_100, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
load("../Programs/Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```{r PlotAO, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_7_AO.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```{r PlotAO_chicago_city, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_chicago_city_512_7_AO_100b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_data_mexico_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_panama_512_5_Ebr_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```{r PlotAO_panama_city, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_Mexico_512_7_AO_300b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
#save(difference_values, x, file = "./Data/results_data_mexico_512_5_Ebr_50b.Rdata")
#save(difference_values, x, file = "./Data/results_data_panama_512_5_Ebr_100b.Rdata")
source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")

```{r, eval=FALSE}
load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
#load("../Programs/Data/results_data_agua_300_7_AO.Rdata")

x2<-as.vector(difference_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```

```{r Plot_EBra, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_E.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_300b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```
```{r Plot_EBra300, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_Eb_300b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_1b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r Plot_EBra1b, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_Eb_1b.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_1b.Rdata

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r Plot_correa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_agua_300_9_correa.Rdata")
#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")

source("../imagematrix.R")
hist(difference_values)

ggplot() +
  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r, eval=FALSE}
#load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
load("../Programs/Data/results_data_agua_300_5_Eb_300b.Rdata")

x2<-as.vector(difference_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```

```{r 2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR", eval=FALSE}
load("../Programs/Data/results_chicago_city_512_7_AO_100b.Rdata")
x1<-as.vector(difference_values)

@@

#fit.weibull <- fitdist(x1, "weibull")
#plot(fit.weibull)
#fit.weibull$aic
 fit.norm <- fitdist(x1, "norm")
 fit.norm$aic
 plot(fit.norm)
```

@@

```{r cv5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
alpha <- 5.452
beta <- 2.061

save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix ))
#plot(imagematrix(p_values_matrix >0.1))
```

```{r cv_lognormal, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
plnorm_inv <- function(x, meanlog, sdlog) {
  pnorm(log(x), mean = meanlog, sd = sdlog)
}

# Cargar los datos y parámetros de ajuste de la distribución lognormal
meanlog <- -0.1931404
sdlog <- 0.4293747

# Crear una matriz para almacenar los p-valores
p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]

    # Calcular el p-valor utilizando la función de distribución acumulativa inversa de la distribución lognormal
    p_values_matrix[i, j] <- plnorm_inv(cv_value, meanlog, sdlog)
  }
}

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
plot(imagematrix(equalize(z.up.le)))
plot(imagematrix(equalize(cv_values)))#z.up.le
plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix <0.1))
plot(imagematrix(p_values_matrix >0.1))
```

```{r cv_lognormal2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
load("../Programs/Data/results_data_simulated_Phantom_7.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
# plnorm_inv <- function(x, meanlog, sdlog) {
#   pnorm(log(x), mean = meanlog, sd = sdlog)
# }

# Cargar los datos y parámetros de ajuste de la distribución lognormal
# Cargar los datos y parámetros de ajuste de la distribución lognormal
meanlog <- -0.1503808
sdlog <-  0.4504363

# Crear una matriz para almacenar los p-valores
p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))

# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
for (i in 1:nrow(cv_values)) {
  for (j in 1:ncol(cv_values)) {
    cv_value <- cv_values[i, j]

    # Calcular el p-valor utilizando la función plnorm()
    p_values_matrix[i, j] <- 1-plnorm(cv_value, meanlog = meanlog, sdlog = sdlog)
  }
}

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
#plot(imagematrix(equalize(z.up.le)))
plot(imagematrix(equalize(cv_values)))#z.up.le
plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix <0.1))
plot(imagematrix(p_values_matrix >0.1))
```

```{r cv_lognormal3_mnad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
load("../Programs/Data/results_data_simulated_z_up_le_mnad_250_7.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
# plnorm_inv <- function(x, meanlog, sdlog) {
#   pnorm(log(x), mean = meanlog, sd = sdlog)
# }

# Cargar los datos y parámetros de ajuste de la distribución lognormal
# Cargar los datos y parámetros de ajuste de la distribución lognormal
meanlog <- -0.2861518
sdlog <- 0.5366815

# Crear una matriz para almacenar los p-valores
p_values_matrix <- matrix(NA, nrow = nrow(cd_values_mnad), ncol = ncol(cd_values_mnad))

# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
for (i in 1:nrow(cd_values_mnad)) {
  for (j in 1:ncol(cd_values_mnad)) {
    cd_value_mnad <- cd_values_mnad[i, j]

    # Calcular el p-valor utilizando la función plnorm()
    p_values_matrix[i, j] <- 1-plnorm(cd_value_mnad, meanlog = meanlog, sdlog = sdlog)
  }
}

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
#plot(imagematrix(equalize(z.up.le)))
plot(imagematrix(equalize(cd_values_mnad)))#z.up.le
plot(imagematrix(p_values_matrix ))
plot(imagematrix(p_values_matrix <0.1))
plot(imagematrix(p_values_matrix >0.05))
```

```{r cv_lognormal3_entropy, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }

load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
# Calcular la media y la desviación estándar de los datos originales
mean_original <- mean(difference_values, na.rm = TRUE)
sd_original <- sd(difference_values, na.rm = TRUE)

# Normalizar los datos
normalized_data <- (difference_values - mean_original) / sd_original

# Parámetros de la distribución normal estándar
mean_standard <- 0
sd_standard <- 1

# Definir función para calcular los p-valores
calculate_p_value <- function(x) {
  p_value <- 2 * pnorm(-abs(x), mean = mean_standard, sd = sd_standard)
  return(p_value)
}

# Dimensiones de la matriz difference_values
n_rows <- nrow(normalized_data)
n_cols <- ncol(normalized_data)

# Matriz para almacenar los p-valores
p_values <- matrix(NA, nrow = n_rows, ncol = n_cols)

# Iterar sobre cada dato en normalized_data y calcular el p-valor correspondiente
for (i in 1:n_rows) {
  for (j in 1:n_cols) {
    p_values[i, j] <- calculate_p_value(normalized_data[i, j])
  }
}

# Guardar los p-valores
#save(p_values, file = "p_values_matrix_normalized.Rdata")

#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
#save(p_values, file = "../Programs/Data/p_values_matrix_normalized.Rdata")
#load("../Programs/Data/p_values_matrix_normalized.Rdata")
# Definir la función de distribución acumulativa inversa de la distribución lognormal
# plnorm_inv <- function(x, meanlog, sdlog) {
#   pnorm(log(x), mean = meanlog, sd = sdlog)
# }

# # Cargar los datos y parámetros de ajuste de la distribución lognormal
# # Cargar los datos y parámetros de ajuste de la distribución lognormal
# # Calcular la media y la desviación estándar de los datos originales
# mean_original <- mean(difference_values, na.rm = TRUE)
# sd_original <- sd(difference_values, na.rm = TRUE)
# 
# # Normalizar los datos
# normalized_data <- (difference_values - mean_original) / sd_original
# 
# # Parámetros de la distribución normal estándar
# mean_standard <- 0
# sd_standard <- 1
# 
# # Definir función para calcular los p-valores
# calculate_p_value <- function(x) {
#   p_value <- 2 * pnorm(-abs(x), mean = mean_standard, sd = sd_standard)
#   return(p_value)
# }
# 
# # Dimensiones de la matriz difference_values
# n_rows <- nrow(normalized_data)
# n_cols <- ncol(normalized_data)
# 
# # Matriz para almacenar los p-valores
# p_values <- matrix(NA, nrow = n_rows, ncol = n_cols)
# 
# # Iterar sobre cada dato en normalized_data y calcular el p-valor correspondiente
# for (i in 1:n_rows) {
#   for (j in 1:n_cols) {
#     p_values[i, j] <- calculate_p_value(normalized_data[i, j])
#   }
# }
# 
# # Guardar los p-valores
# save(p_values, file = "../Programs/Data/p_values_matrix_normalized_1.Rdata")

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

# Guardar la matriz de p-valores
#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")

#source("../imagematrix.R")
source("../imagematrix.R")
#hist(p_values_matrix)
#par(mfrow=c(1,2))
#plot(imagematrix(p_values_matrix ))
#plot(imagematrix(equalize(z.up.le)))
#plot(imagematrix(equalize(cd_values_mnad)))#z.up.le
plot(imagematrix(p_values ))
plot(imagematrix(p_values <0.1))
plot(imagematrix(p_values >0.5))
```

```{r, eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
x2<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```
```{r cv7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 7x7, Flevoland", eval=FALSE}
load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
alpha <- 5.762
beta <- 2.611

@@

source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.05))
valores_menores_que_0_05 <- sum(p_values_matrix < 0.05)
cat("Número de valores menores que 0.05:", valores_menores_que_0_05, "\n")

@@

```{r cvOttawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa", eval=FALSE}

@@

source("../imagematrix.R")
hist(p_values_matrix)
par(mfrow=c(1,2))
#plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
plot(imagematrix(p_values_matrix >0.05))
```

@@

```{r cqvOttawa_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa", eval=FALSE}

@@

source("../imagematrix.R")
#hist(p_values_matrix)
par(mfrow=c(1,2))
plot(imagematrix(equalize(x)))
plot(imagematrix(p_values_matrix))
#plot(imagematrix(p_values_matrix <0.05))
```

```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

@@

ggplot() +
  geom_density(aes(x = as.vector(cd_values_mad)), fill = "pink", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r 5ottawa_mad, eval=FALSE}
load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_5.Rdata")
x2<-as.vector(cd_values_mad)
mydata_dist <- univariateML::model_select(x2)
mydata_dist
```

```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }

load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_7.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cd_values_mad)), fill = "blue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

### 2024-05-07 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
doctoral qualification document

---
title: Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy
affiliation:

@@

Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
We used $7 \times 7$ local sliding windows for the test. 
In Fig. \ref{fig:Real_SAR_Images}(b), the heatmap of the $p$-values refers to the decisions at the $5\%$ significance level, with the orange areas representing a rejection of the null hypothesis, i.e., heterogeneous areas, while the blue areas representing non-rejection at the $5\%$ significance level, indicating homogeneity.
```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.    ' ), out.width = c("40mm", "59mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
knitr::include_graphics("../../../Figures/PDF/pvalue_f.pdf")

>>>>

---
title: Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy
affiliation:

@@

Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
We used $7 \times 7$ local sliding windows for the test. 
Fig.&nbsp;\ref{fig:Real_SAR_Images}(b) shows the heatmap of the $p$-values.
The color table maps all above $0.05$ into dark blue (no evidence to reject the fully-developed speckly hypothesis), and those below  $0.05$ into a gradient between blue and orange (evidence to reject the hypothesis).

```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.    ' ), out.width = c("40mm", "59mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
knitr::include_graphics("../../../Figures/PDF/pvalue_f.pdf")
```

These results show that the map of $p$-values correctly identify regions with different levels of heterogeneity.
